An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-20 article.tex
Tabular fixes

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

@@

      \begin{keyword}
      %% keywords here, in the form: keyword \sep keyword
      keyword one \sep keyword two
      %% PACS codes here, in the form: \PACS code \sep code
      \PACS 0000 \sep 1111
      %% MSC codes here, in the form: \MSC code \sep code
      %% or \MSC[2008] code \sep code (2000 is the default)
      \MSC 0000 \sep 1111
      \end{keyword}

@@

  %\centering
    %\begin{center}

@@

           & Response & Predictors & Covariates & Interactions \\ \midrule
          Model 1 & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\

@@

          Model 2 & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope 1 Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\

@@

          Model 3 & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\

@@

          Model 4 & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope 1 Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}

@@

    %\end{adjustbox}
    %\end{center}

@@

Models were validated using K-fold cross validation calculated through the R Caret Package \citep{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times. % A reference for this is absolutely needed.

@@

($< 2.200E-16$, see Tables ?? and ??)

@@

  \caption{Summary of models; their performance, F-statistics and Residual error.}
      \label{tab:modelsummary}
      \resizebox{\textwidth}{!}{\begin{tabular}{@{}cccccccc@{}}

@@

          & \textbf{$R^2$}       & \textbf{$Adjusted R^2$} & \textbf{F-statistic} & \textbf{P-Value}     & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule

@@

        \multicolumn{1}{l}{}                                                  & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}    & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}                                                       & \multicolumn{1}{l}{}                                                       & \multicolumn{1}{l}{}                                                        \\

@@

        \multicolumn{1}{l}{}                                                  & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}    & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}                                                       & \multicolumn{1}{l}{}                                                       & \multicolumn{1}{l}{}                                                        \\
        \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ Value/Area\end{tabular}} & 9.669E-01            & 9.638E-01               & 3.095E+02            & 2.200e-16            & 1.904E-01                                                                  & 9.528E+01                                                                  & 4.000E-02                                                                   \\ \bottomrule

@@

Each model showed a strong relationship between the predictors and the response (see Table \ref{tab:modelsummary}). The strength of the models was measured in $R^2$, as this allowed an easy comparison between their performances and their validation. 

>>>>

%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

@@

      \begin{keyword}
      %% keywords here, in the form: keyword \sep keyword
      Keyword one \sep{} keyword two
      %% PACS codes here, in the form: \PACS code \sep code
      \PACS{} 0000 \sep{} 1111
      %% MSC codes here, in the form: \MSC code \sep code
      %% or \MSC[2008] code \sep code (2000 is the default)
      \MSC{} 0000 \sep{} 1111
      \end{keyword}

@@

@@

          & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
          \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\

@@

          \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope 1 Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\

@@

          \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\

@@

          \textbf{Model 4} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope 1 Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope 1 Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}

@@

@@

Models were validated using K-fold cross validation calculated through the R Caret Package \citep{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times.
% A reference for this is absolutely needed.

@@

($< 2.200E-16$, see Tables  and )

@@

  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}

@@

           & $\mathbf{R^2}$ & $\mathbf{R^2}$ & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule

@@

@@

          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ Value / Area\end{tabular}} & 9.669E-01 & 9.638E-01 & 3.095E+02 & 2.200e-16 & 1.904E-01 & 9.528E+01 & 4.000E-02 \\ \bottomrule
        }

@@

Each model showed a strong relationship between the predictors and the response (see Table~\ref{tab:modelsummary}). Model accuracy was measured in $R^2$, as this allowed an easy comparison between their performances and their validation.
